---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(MASS)
library(ISLR)
```

# Simple Linear Regression

```{r echo=FALSE}
names(Boston)
plot(medv~lstat, Boston)
abline(fit1, col='red')
```

*lstat* has a significant p-value means that an important variable for the model.
```{r}
fit1 <- lm(medv ~lstat, data=Boston)
fit1
summary(fit1)
```

```{r}
names(fit1)
confint(fit1)
```

```{r}
predict(fit1, data.frame(lstat=c(5,10,15)), interval = 'confidence')
```

# Multiple Linear Regression

```{r}
fit2 <- lm(medv~lstat+age, data = Boston)
summary(fit2)
```

```{r}
fit3 <- lm(medv~., Boston)
summary(fit3)
```

When we look at the fitted model with all variables, we see yhat age is not significant anymore.

```{r}
par(mfrow=c(2,2))
plot(fit3)
```

```{r}
fit4 <- update(fit3, ~.-age-indus)
summary(fit4)
```

Once we removed age and indus variables, the updated model shows that the rest of the variables are significant.

# Nin Linear terms & interactions

```{r}
fit5 <- lm(medv~lstat*age, Boston)
summary(fit5)
```

```{r}
fit6 <- lm(medv~lstat +I(lstat^2), Boston); summary(fit6)
```

linear and the quadratic form of lstats are important for the fitted model.
```{r}
attach(Boston)
par(mfrow = c(2,1))
plot(medv~lstat)
points(lstat, fitted(fit6), col='red', pch=20)

```

```{r}

fit7 <- lm(medv~poly(lstat,4))
points(lstat, fitted(fit7), col = 'blue', pch = 20)
```


# Qualitative Predictors

```{r}
fix(Carseats)
names(Carseats)
summary(Carseats)
```

```{r}
fit8 <- lm(Sales~.+Income:Advertising+Age:Price, Carseats)
summary(fit8)
```

```{r}
contrasts(Carseats$ShelveLoc)
```
```{r}
regplot <- function(x,y,...){
  fit <- lm(y~x)
  plot(x,y,...)
  abline(fit, col='red')
  
}
```

```{r}
attach(Carseats)
regplot(Price, Sales)
```

```{r}
regplot(Price, Sales, xlab="Price", ylab="Sales", col ='blue')
```




